### 2022-01-18 src-latex/parts/60-results.tex
Add fig. on ner vs ocr noise

\begin{table}
\caption{CamemBERT and CamemBERT-pretrained NER performances at entry-level on manually corrected and noisy OCRerd entries when fine-tuned on manually corrected entries.}
\begin{tabular}{lrrrrrrrrr}
Model & \multicolumn{3}{c}{Camembert.pretrained} & \multicolumn{3}{c}{Camembert} & \multicolumn{3}{c}{Camembert.pretrained} \\
Train set & \multicolumn{3}{c}{ref} & \multicolumn{3}{c}{ref} & \multicolumn{3}{c}{pero-ocr} \\
Test set &                  ref & pero-ocr & tesseract &       ref & pero-ocr & tesseract &                  ref & pero-ocr & tesseract \\
\midrule
Precision &                 96.5 &     93.3 &      90.3 &      96.1 &     92.4 &      89.7 &                 94.3 &     93.6 &      89.9 \\
Recall    &                 96.5 &     92.6 &      91.3 &      96.6 &     92.5 &      91.2 &                 96.1 &     94.5 &      92.5 \\
F1 score        &                 96.5 &     92.9 &      90.8 &      96.4 &     92.5 &      90.5 &                 95.2 &     94.1 &      91.2 \\
\end{tabular}
\end{table}

Opt. use synthetic text perturbation as well? Maybe not interesting and too artificial if we have access to 2+ OCR systems.
(original OCR from BNF, Tesseract 4, Pero OCR…)

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{src-latex/figs/eval-ner-exp2.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing data, either manually corrected or OCRed with Pero-OCR and Tesseract. The type of examples used to train the NER task is noted in indice after the model name (e.g. Bert$_{reference}$). Results show that best performances on OCRed entries are obtained when the BERT model has been pretrained and fine-tuned for NER on examples affected with similar OCR errors.}
    \label{fig:exp_2_eval_ner}
\end{figure}
Opt. use synthetic text perturbation as well? Maybe not interesting and too artificial if we have access to 2+ OCR systems.
(original OCR from BNF, Tesseract 4, Pero OCR…)
